\documentclass[]{article}

\usepackage{hyperref}
\usepackage[utf8]{inputenc}

\title{Creating a Voxel Based Game}
\author{Felix Bärring}

\begin{document}

\maketitle

\begin{abstract}
	
The purpose of this project is to create voxel based game, similar to games such as Infiniminer. The most characteristic feature is the abillity to modify the world by removing and adding cubes. The player can move around in a semingly infinite world, exploring and creating content. To make this possible components such as rendering, colission detection, and procedural terrain generation must be implemented. Other components that can be relevant are, artificall inteligence and multiplayer.

\end{abstract}

\section{Motivation and Background}

My Bachelor Thesis (available here {\url{https://gupea.ub.gu.se/handle/2077/39606}) was about creating a voxel game engine in Java using OpengGL, together with five other students. Although we were successfull with reaching our goals, there were severall aspects of the implementation that I think could have been done better. As I am interested in learing C++, I figured that doing a similar project in C++ instead of Java would be a good way to learn the language and various other topics, such as computer graphics and OpenGL.

\section{Goals}

My maing goal with this project will be about learingin as much as possible, if the game happens to be enyoable that would oufcourse be good, but it is not the main consern. The primary focus will be on rendering and world interaction. When those areas have been implemented other aspects such as Terrain Generation, AI, Audio, and GUIs will hopefully be implemented. I intend to make demos that showcase all the implemented functionality in isolation from other features, and also write short documentation on the subject.

\end{document}
